\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-04-09 doc/USER_MANUAL/manual_SPECFEM3D.tex
rephrased and shortened the paragraph about Discontinuous Galerkin

Note that in most geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies, in which very high frequencies or supershear rupture need to be modeled near the fault, see e.g. \cite{BeGlCrViPi07,BeGlCrVi09,PuAmKa09,TaCrEtViBeSa10})
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient;
conforming mesh doubling bricks can efficiently handle mesh size variations \citep{KoTr02a,KoLiTrSuStSh04,LeChLiKoHuTr08,LeChKoHuTr09,LeKoHuTr09}.
Also, without significant modifications in the complexity of the
discontinuous technique \citep{CaKaBr10,SmCoObOvSch10},
usually those methods need to assume constant material properties inside
each element, while the SEM can handle gradients inside each element.\\

>>>>

Note that in many geological models in the context of seismic wave propagation studies
(except for instance for fault dynamic rupture studies, in which very high frequencies or supershear rupture need to be modeled near the fault, see e.g. \cite{BeGlCrViPi07,BeGlCrVi09,PuAmKa09,TaCrEtViBeSa10})
a continuous formulation is sufficient because material property contrasts are not drastic and thus
conforming mesh doubling bricks can efficiently handle mesh size variations \citep{KoTr02a,KoLiTrSuStSh04,LeChLiKoHuTr08,LeChKoHuTr09,LeKoHuTr09}.\\
